Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-07-22 manuscript/climate_sensitivity_SI.Rmd
Fixed placement of package citations #129

---
title: ""
author: ""
output:
  pdf_document:
    fig_caption: yes
bibliography: ["packages.bib"]
biblio-style: apalike
csl: new-phytologist.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{setspace}\onehalfspacing
- \captionsetup[figure]{labelformat=empty}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
---

@@

### Supplementary Information
## Tree height and leaf drought tolerance traits shape growth responses across droughts in a temperate broadleaf forest

@@

\listoftables
\listoffigures

\newpage
While there were several R-packages we used for a specific purpose in our methods, numerous packages were immensely helpful for this research behind the scenes. As in all of science, this study is a representation of the work done by both the authors of this paper as well as countless others. While acknowledging everyone is impossible, we want to at least give thanks to those who made this work possible.

@@

>>>>

---
title: ""
author: ""
output:
  pdf_document:
    fig_caption: yes       
    includes:  
      in_header: preamble-latex.tex
bibliography: ["packages.bib"]
biblio-style: apalike
csl: new-phytologist.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{setspace}\onehalfspacing
- \captionsetup[figure]{labelformat=empty}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
---

@@

# Supplementary Information
## Tree height and leaf drought tolerance traits shape growth responses across droughts in a temperate broadleaf forest

@@

\listoftables
\listoffigures
\newpage

@@

\newpage
## Further Package Citations
While there were several R-packages we used for a specific purpose in our methods, numerous packages were immensely helpful for this research behind the scenes. As in all of science, this study is a representation of the work done by both the authors of this paper as well as countless others. While acknowledging everyone is impossible, we want to at least give thanks to those who made this work possible.
